### 2016-02-08 docs/ms_communitySynchrony.Rmd
updates abstract; calculates avg synchrony and year effects

Abstract
-------------
Temporal asynchrony among interacting species is an important mechanism through which species richness can stabilize biomass production through time. 
While asynchrony is a key mechanism linking biodiversity and ecosystem function, empirical support for the prevalance of species asynchrony is mixed, and no studies have rigorously disentangled the forces driving species (a)synchrony in nature. 
We use stochastic, multi-species population models fit using long term datasets from five semi-arid grasslands to determine the relative importance of the three forces that drive species synchrony: environmental fluctuations, interspecific competition, and demographic stochasticity.
Species' environmental responses were positively, but not perfectly correlated. 
As a result, community-wide synchrony was higher when environmental variation was present rather than absent, but synchrony was not perfect.
Removing interspecific competition, which was weak in all communities, did not affect synchrony, and demographic stochasticity only played a role in small populations.
Our results suggest that all five communities represent the theoretical limiting case where demographic stochasticity and competition are weak, and community-wide synchrony is approximately equal to the synchrony of species' environmental responses -- a result that may be quite general if natural communities tend to have large niche differences among species.
However, our results are in contrast to a recent analysis of several biodiversity-ecosystem function experiments, suggesting an interplay between community assembly and the drivers of community synchrony.

>>>>

Abstract
-------------
Temporal asynchrony among interacting species is an important mechanism through which species richness can stabilize biomass production through time. 
While asynchrony is a key mechanism linking biodiversity and ecosystem function, empirical support for the prevalance of species asynchrony is mixed, and no studies have rigorously disentangled the forces driving species (a)synchrony in nature. 
We used stochastic, multi-species population models fit using long term datasets from five semi-arid grasslands to determine the relative importance of the three forces that drive species synchrony: environmental fluctuations, interspecific competition, and demographic stochasticity.
Species' environmental responses, quantified as temporal random effects in vital rate regressions, were positively correlated in each community, ranging from $\rho = 0.23$ to $\rho = 0.38$ when averaged over vital rates. 
As a result, community-wide synchrony of per capita growth rates ($\phi_r$), which ranges from 0 (perfect asynchrony) to 1 (perfect synchrony), was higher when environmental variation was present (average $\phi_r = 0.62$) rather than absent (average $\phi_r = 0.43$).
Removing interspecific competition, which was weak in all communities, did not affect synchrony, and demographic stochasticity only played a role in small populations.
Our results suggest that all five communities represent the theoretical limiting case where demographic stochasticity and competition are weak, and community-wide synchrony is approximately equal to the synchrony of species' environmental responses -- a result that may be quite general if natural communities tend to have large niche differences among species.
However, our results are in contrast to a recent analysis of several biodiversity-ecosystem function experiments, suggesting that strong transient competition early in community assembly can counteract the often synchronizing effect of environmental fluctuations.
